---
title: "asymmetric_mobility_intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{asymmetric_mobility_intro}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spread)
```

## Required data

The initial values for all geographic locations.

```{r}
spread::asymmetric_mobility_dummy_seiiar_pop
```

A list containing 1 mobility matrix per time period (4 time periods per day, 5 days = 20 time periods).

The mobility matrix must contain all non-diagonal links (i.e. every geographical location combination must be included, except for people "staying at home")

```{r}
length(spread::asymmetric_mobility_dummy_mobility_matrix)
spread::asymmetric_mobility_dummy_mobility_matrix[[1]]
```

One beta per time period.

```{r}
spread::asymmetric_mobility_dummy_betas
```

## Example

```{r}
d <- spread::asymmetric_mobility(
  seiiar_pop = spread::asymmetric_mobility_dummy_seiiar_pop,
  mobility_matrix = spread::asymmetric_mobility_dummy_mobility_matrix,
  betas = spread::asymmetric_mobility_dummy_betas,
  latent_period = 1.9,
  infectious_period = 3.0,
  asymptomatic_prob = 0,
  asymptomatic_relative_infectiousness = 0,
  N = 1
)
```

`b_*` variables represent the status of people belonging to a particular geographical location.

`c_*` variables represent the current status of all the people existing in that geographical location at that time point.

```{r}
print(d)
```
