---
title: "Simple Branching Process model"
author: "Gunnar Rø"
date: "2020-01-31"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{branching_process}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Background

We show how to use the branching process model by modelling the potential spread of SARS-like corona virus. The branching process model takes information about the basic reproduction number, the serial interval and a dispersion parameter and can make short term forecasts of the number of new cases. The current model does not take into account depletion of suceptibles or the introduction of any control measures.

Following [Lipsitch et Al 2003](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2760158) we use a value for R0 of 3 and a serial interval with mean 8.4 days and SD 3.4 days. We also set the dispersion parameter to 0.16 following [Lloyd-Smith et Al 2005](https://www.nature.com/articles/nature04153).

```{r message=FALSE, warning=FALSE, fig.height=5, fig.width=7}
library(ggplot2)
library(epitrix)

#Defining the serial interval

mu <- 8.4
sd <- 3.4
param <- epitrix::gamma_mucv2shapescale(mu, sd/mu)
si <-   distcrete::distcrete("gamma", interval = 1,
                shape = param$shape,
                scale = param$scale, w = 0)


incidences <- spread::branching_process(initial_cases=1,                
                         R0=1.4,
                         dispersion=1,
                         serial_interval=si,
                         days_simulation=30,
                         simulations=1000)
summary <- spread::summarize_bp(incidences)
spread::plot_quantiles_bp(incidences) + ggtitle("Estimated daily incidence") + xlab("Days") + ylab("Incidence")
spread::plot_quantiles_bp(summary$cumulative) + ggtitle("Estimated cumulative case counts")  + xlab("Days") + ylab("cumulative Cases")

ggplot() + geom_histogram(aes(x=colSums(incidences))) +theme_minimal() +ggtitle("Distribution of number of cases after 30 days") + xlab("N cases after 30 days") 

print(median(summary$cumulative[30,]))
print(summary$p_no_spread)

``` 

The median number of cases is around 50, with a probability of no spread is around 6%. 

# Estimating parameters via approximate Bayesian computation (ABC)

We can also estimate the R0 if we know the number of cases after a time t. Here we will assume that there are between 2000 and 4000 cases after 56 days. One can also here vary the other parameters to include uncertainty in them

```{r}
mu <- 8.4
sd <- 3.4
param <- epitrix::gamma_mucv2shapescale(mu, sd/mu)
si <-   distcrete::distcrete("gamma", interval = 1,
                shape = param$shape,
                scale = param$scale, w = 0)
params <- list()
for(R0 in seq(from=1, to=10, by=0.05)){
    params[[length(params)+1]] <- list(
      initial_cases=1,                
      R0=R0,
      dispersion=1,
      serial_interval=si,
      days_simulation=56
    )
}

r <- spread::fit_params_bp(
  cases_min = 2000,
  cases_max = 3000, 
  param_list = params, 
  simulations=1000
  )
print(HDInterval::hdi(r$R0))
```

